# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r}
unzip("activity.zip", "activity.csv")
data <- read.csv("activity.csv")
data <- transform(data, date = as.Date(date))
```


## What is mean total number of steps taken per day?
```{r fig.width=6, fig.height=6}
sumsteps <- aggregate(data$steps, list(date=data$date), sum)
hist(sumsteps$x, col="cyan")
summary(sumsteps$x)[c("Median", "Mean")]
```


## What is the average daily activity pattern?
```{r fig.width=6, fig.height=6}
meanstepsbyinterval <- aggregate(data$steps, 
                                 list(interval=data$interval), 
                                 mean, na.rm=T)
plot(meanstepsbyinterval$interval, 
     meanstepsbyinterval$x, 
     type="l")

```

Interval with most steps: 
```{r fig.width=6, fig.height=6}
meanstepsbyinterval[meanstepsbyinterval$x == max(meanstepsbyinterval$x), "interval"]
```


## Imputing missing values
Total number of rows with NAs: 
```{r} 
sum(is.na(data$steps))
```

We will supply the missing values by filling them in from the interval averages.
```{r}
data.imputed <- data
for (i in which(is.na(data.imputed$steps))) {
  interval <- data.imputed$interval[i]
  impute <- meanstepsbyinterval[
      meanstepsbyinterval$interval == interval, "x"]
  data.imputed$steps[i] <- impute
}
```

```{r fig.width=6, fig.height=6}
sumsteps.imputed <- aggregate(data.imputed$steps, 
                              list(date=data.imputed$date), sum)
hist(sumsteps.imputed$x, col="pink")
summary(sumsteps.imputed$x)[c("Median", "Mean")]
```



## Are there differences in activity patterns between weekdays and weekends?
```{r}
data.imputed$weekday <- weekdays(data.imputed$date)
data.imputed$weekday.type <- factor(lapply(data.imputed$weekday, function(day) {if (day == "Saturday" || day == "Sunday") { "weekend" } else { "weekday" }}), c("weekend", "weekday"))
```
